Homework 5 Case Study Question 1


```{r}
library(ggpubr) #helps us to create results that are publication ready for your report
library(tidyverse) #for data manipulation and visualization
library(broom) #tidy model output
library(gclus) #Allows us to have our scatterplot with correlation embedded in it
theme_set(theme_pubr())
```

```{r}
bank_df <- read.csv("Documents/BUS2_194A_Statistical_Analysis/Chapter_15/HW5_Bank.csv")
head(bank_df) #Gives us a snapshot of the excel file 
``` 
=> headshot of the dataset 


```{r}
plot(bank_df$Balance, bank_df$Direct, main = "Scatter plot", xlab = "average monthly checking account balance ",
     ylab = "whether the customer contacted signed up for payroll direct deposit", pch = 19) 

ggplot(bank_df, aes(Balance, Direct)) + 
  geom_point() + 
  stat_smooth(method = glm, se = FALSE,method.args = list(family=binomial), col = "green")
```
=> interpretation of the scatter plot: values of E(y) range from 0 to 1 and that the curve is S-shaped makes our equation ideally suited to model the probability the dependent variable is equal to 1. Also note that the value of E(y) gradually approaches 1 as the value of x becomes larger. 


```{r}
bank_logit <- glm(Direct ~ Balance, data = bank_df, family = "binomial")
summary(bank_logit)
```
=> interpretation: based on summary statistics, our equation is y hat = (e^-2.633+0.22x)/(1 + e^-2.633+0.22x), the intercept (Bo) is -2.633 and the slope (B1) is 0.22. 

```{r}
newdatabank_df<-read.csv("Documents/BUS2_194A_Statistical_Analysis/Chapter_15/newdatabank.csv")
newdatabank_df
```
=> prediction 

```{r}
prediction <- predict(bank_logit, newdata = newdatabank_df, type = "response") 
prediction
```
=> probability 

```{r}
prediction <- predict(bank_logit, data = bank_df, type = "response") 
prediction
```

=> the average monthly balance should be $1200 or more to achieve 0.5 or higher probability of signing up for direct payroll deposit 

```{r}
exp(cbind(OR = coef(bank_logit), confint(bank_logit, level = 0.95))) #odds ratio
```
=> interpretation: the estimated odds ratio for Balance is 1.25, which means that the estimated odds of signing up for direct payroll deposit is 1.25 times greater for any one-unit change in Balance variable. Furthermore, the range of confidence interval does not contain the value of 1 which indicates that Balance has a significant relationship with the estimated odds ratio. 

however, for any increase of more than one unit for Balance variable, we would need to investigate the relationship between the odds ratio and the regression coefficients. 
```{r}
exp(5*0.22)
```
=> for example, this output tells us that the estimated odds of signing up for direct payroll deposit is 3 times greater for any 5-unit change in Balance variable, i.e. the estimated odds ratio for an increase of $500 in account balance is 3. 

